The player set is denoted by $N=\{1,\dots,n\}$. Each player $i\in N$ selects a pure strategy $x_i$ from a nonempty compact set $X_i\subseteq \R^{d_i}$, where $d_i$ is a positive integer. A~pure strategy profile is the $n$-tuple $\bx=(x_1,\dots,x_n)\in \bX$, where $\bX=X_1\times\dots\times X_n$. We assume that each utility function $u_i\colon \bX\to \R$ is continuous. A \emph{continuous game} is the tuple
\[
	\calG=\langle N,(X_i)_{i\in N},(u_i)_{i\in N}\rangle.
\]

A mixed strategy of player $i$ can be an arbitrary Borel probability measure $\mu_i$ over $X_i$. Note that this general framework allows us to consider mixed strategies whose support is uncountably infinite, which is inevitable for the coherent treatment of games over compact strategy sets.

By $M_i$ we denote the space of all mixed strategies of player $i\in N$. Let $\bM=M_1\times \dots \times M_n$ and let $\bmu=(\mu_1,\dots,\mu_n) \in \bM$ be a profile of mixed strategies. For the sake of brevity, we use $\bmu$ in place of the corresponding product probability measure $\mu_1\times\dots\times \mu_n$ in the definitions below involving integrals. The expected utility of player $i\in N$ is the function $U_i\colon \bM\to \R$
\[
    U_i(\bmu) =  \int_{\bX} u_i \dif\bmu
\]
This definition yields a function $U_i\colon \bM\to \R,$ which can be effectively evaluated only in special cases, such as when the support of each $\mu_i$ is finite.

We define the sets which exclude one player as
\[
\bX_{-i}=\bigtimes_{\substack{j\in N \\ j\neq i}} X_j \quad \text{and} \quad \bM_{-i}=\bigtimes_{\substack{j\in N \\ j\neq i}}M_j.
\]
For every $\bmu\in \bM$ and each player $i\in N$, by $\bmu_{-i}$ we denote the restriction of $\bmu$ onto $\bM_{-i}$.  The value of expected utility of player $i$ in a strategy profile $(x_i,\bmu_{-i})\in X_i\times \bM_{-i}$ is denoted by
\begin{equation}\label{def:EU}
    U_i(x_i,\bmu_{-i})=\int_{\bX_{-i}} u_i(x_i,.)\; \dif\bmu_{-i}.
\end{equation}

\begin{definition}[\textcite{Nash51}]\label{def:ne}
    A Nash equilibrium is a strategy profile $\bmu^\star\in\bM$ satisfying
    \begin{equation*}
        U_i(\bmu^\star)=\max_{x_i\in X_i} U_i(x_i,\bmu_{-i}^\star), \qquad \forall i\in N.
    \end{equation*}
    That is, each player's strategy is a best response against those of the others.
\end{definition}

\begin{theorem}[\textcite{Glicksberg52}]\label{thm:Glick}
    Every continuous game has a mixed strategy Nash equilibrium.
\end{theorem}